Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/discussions.tex

\paragraph{Regularity of the value function}~In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This is a strong
hypothesis that is not always verified in practice. Very simple environments
break this hypothesis, such as for instance, the pendulum swing up environment,
with pendulum height as reward and torque as action.  Indeed, assume that $\pi$
is the optimal policy for the pendulum swing up environment, with state
representation $(\theta, \dot{\theta})$. The state space for this environment
can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
$\mathcal{G}$ the subspace where when following the optimal policy, the
pendulum can be swang up without crossing the $y$-axis, and $\mathcal{B}$ where
it have to cross the $y$-axis. The difference of V-function between a point in
$\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
quantity $M$. Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
such that $s_1$ and $s_2$ are arbitrarily close. Consequently, $V^\pi$ is
discontinuous on the frontier, which results in non infinitesimal advantages
for actions taken on the frontier. \TODO{Non infinitesimal advantages are found,
	more generally, as soon as a given policy has different regimes, depending on
	where it starts in state space. For such policies, at the frontier between two regimes,
the value function can be discontinuous, resulting in non infinitesimal advantages.}

>>>>

\paragraph{Smoothness of the value function.} In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This %is a strong
hypothesis is not always satisfied in practice. Very simple environments
break this hypothesis, such as the pendulum swing-up environment,
with pendulum height as reward and torque as action.  Indeed, 
% assume that $\pi$
% is the optimal policy for the pendulum swing-up environment, with state
% representation $(\theta, \dot{\theta})$. 
the state space $(\theta, \dot{\theta})$ for this environment
can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
$\mathcal{G}$ the subspace where the optimal policy 
can swing up the pendulum without crossing the $y$-axis, and $\mathcal{B}$ where
it has to cross the $y$-axis. The difference of $V$-function between a point in
$\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
quantity. 
%Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
%such that $s_1$ and $s_2$ are arbitrarily close.
Consequently, $V^\pi$ is
discontinuous on the frontier between $\mathcal{G}$ and $\mathcal{B}$, which results in non infinitesimal advantages
for actions taken on the frontier. \TODO{Non infinitesimal advantages are found,
	more generally, as soon as a given policy has different regimes, depending on
	where it starts in state space. For such policies, at the frontier between two regimes,
the value function can be discontinuous, resulting in non infinitesimal advantages.}
